GNSS displacement detection based on Bayesian inference

### 2020-11-13 paper/manuscript.tex
add Prior

\subsubsection{Priors}
\begin{equation}\label{eq_bayesian_prior}
P({\bf{\theta }}) = P({\bf{\tau }},{\bf{\mu }},\sigma ) = P({\bf{\tau }})P({\bf{\mu }})P(\sigma )
\end{equation}
\begin{equation}\label{eq_bayesian_prior_sigma}
\sigma  \sim N({\mu _\sigma },{\sigma _\sigma })
\end{equation}
\begin{equation}\label{eq_bayesian_prior_mu}
{\mu _i} \sim N({\mu _\mu },{\sigma _\mu })(i = 0,1, \cdots ,n)
\end{equation}
\begin{equation}\label{eq_bayesian_prior_mu_sum}
P({\bf{\mu }}) = \prod\limits_{i = 0}^n {P({\mu _i})}
\end{equation}

>>>>

\subsubsection{Prior Distribution}
Assuming that the parameters ${\bf{\tau }}=(\tau_1,\mu_2,\cdots,\tau_n)$, ${\bf{\mu }}=(\mu_0,\mu_1,\cdots,\mu_n)$ and $\sigma$ are independent of each other, then:

\begin{equation}\label{eq_bayesian_prior}
P({\bf{\theta }}) = P({\bf{\tau }},{\bf{\mu }},\sigma ) = P({\bf{\tau }})P({\bf{\mu }})P(\sigma )
\end{equation}
The posterior distribution consists of three parts, including the prior distribution of change point, mean value and standard deviation.

\begin{equation}\label{eq_bayesian_prior_sigma}
\sigma  \sim N({\mu _\sigma },{\sigma _\sigma })
\end{equation}

\begin{equation}\label{eq_bayesian_prior_mu}
{\mu _i} \sim N({\mu _\mu },{\sigma _\mu })(i = 0,1, \cdots ,n)
\end{equation}

\begin{equation}\label{eq_bayesian_prior_mu_sum}
P({\bf{\mu }}) = \prod\limits_{i = 0}^n {P({\mu _i})}
\end{equation}
